Does an earthquake “know” how big it will be? A neural-net aided study

### 2024-05-20 article.tex
Perhaps done with methods?

\subparagraph{Spatially varying Gutenberg Richter}
\subsection{Measurement of temporal incompleteness}

@@

\newpage
\renewcommand\refname{Methods References}
\begin{thebibliography}{10}
\bibitem{zlydenko_neural_2023}
Zlydenko, O. et al. A neural encoder for earthquake rate forecasting. Sci Rep 13, 12350 (2023).
\end{thebibliography}

>>>>

\subparagraph{Spatially varying Gutenberg Richter} Estimation of the local $\beta$ value is done by following the method of \cite{taroni_highdefinition_2021}. Seismicity data is first binned into $0.1^\circ \times 0.1^\circ$, where the GR distribution is calculated for. beta for a specified location $x_i$ calculated by smoothing the binned values over a radius of 30km around $x_i$. Estimation which consider less than 100 events are discarded.

\subsection{Measurement of temporal incompleteness}
Temporal incompleteness is measured at the times of events by fitting the completeness magnitude to a window of 300 events: 150 past events, 1 current event, 149 future events. The window is constructed by the same algorithm, described to construct the \textit{ Last $n$ events benchmark}.

@@

\newpage
\renewcommand\refname{Methods References}
\begin{thebibliography}{10}
\bibitem{zlydenko_neural_2023}
Zlydenko, O. et al. A neural encoder for earthquake rate forecasting. Sci Rep 13, 12350 (2023).
\bibitem{taroni_highdefinition_2021}
Taroni, M., Zhuang, J. \& Marzocchi, W. High‐Definition Mapping of the Gutenberg–Richter b‐Value and Its Relevance: A Case Study in Italy. Seismological Research Letters 92, 3778–3784 (2021).

\end{thebibliography}
